Dynein walks like an Imperial AT-ST

### 2017-12-05 papers/paper/paper.tex
shorten title and change filename
reorder figure slightly

\subsection*{Results}

@@

\begin{figure}%[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/total_step_time_vs_step_length_multiple_seeds}
\caption{Histogram of duration and length of steps taken by model.}
\label{fig:timehist}
\end{figure}

@@

See schematic in Figure~\ref{fig:modelangles}.

>>>>

\section{Results}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{../../plots/time-vs-length-multiple-seeds}
\caption{Histogram of duration and length of steps taken by model.}
\label{fig:duration-length}
\end{figure}

Figure~\ref{fig:duration-length} shows the frequency of steps with
various combination of step length and step time.  We can see that...

@@

@@
